Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-18 paper/main.tex
add supplement section for amir details
- shows data and snapshots
- should be extended to include some formulae and explanations

>>>>

%###################################################################################################
\subsection{Experimental Setup of Amir et. al}

\textbf{TODO explain some of the derivations for the flow profile etc.}

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/progressions/step4-000010.png}
        \node at (0.02,17pt)[anchor=north west, white, draw, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/progressions/step4-000017.png}
        \node at (0.02,17pt)[anchor=north west, white, draw, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/progressions/step4-000034.png}
        \node at (0.02,17pt)[anchor=north west, white, draw, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}\\
    \vspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/result-full/0000000000.png}
        \node at (0.02, 0.98)[anchor=north west, rectangle, draw, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/result-full/0000000001.png}
        \node at (0.02, 0.98)[anchor=north west, rectangle, draw, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.3\textwidth]
        {figures/crm_amir/result-full/0000000002.png}
        \node at (0.02, 0.98)[anchor=north west, rectangle, draw, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}%
    \caption{
        (A-C) Images by Amir et. al~\cite{Amir2014_2} which have been manually segmented.
        The red line within the mask represents the extracted positions.
        (D-F) Snapshots of the numerical simulation showing the rod in its initial, fully bent and
        fully relaxed state.
    }
\end{figure}
